Quasi-Monte Carlo Methods: What, Why, and How?

### 2024-10-21 HickernellMCQMC2024_QMCTutorial.tex
M3 Mac updates

\keywords{}
\end{abstract}
%
\section{Fixed-Period Problems: The Sublinear Case}
%
With this chapter, the preliminaries are over, and we begin the search
for periodic solutions to Hamiltonian systems. All this will be done in
the convex case; that is, we shall study the boundary-value problem
\begin{eqnarray*}
  \dot{x}&=&JH' (t,x)\\
  x(0) &=& x(T)
\end{eqnarray*}
with $H(t,\cdot)$ a convex function of $x$, going to $+\infty$ when
$\left\|x\right\| \to \infty$. We also want to test various things such as whether $\setN$ and $\var(\bsbeta)$ or $\bsu$ are correctly working.

%
\subsection{Autonomous Systems}
%
In this section, we will consider the case when the Hamiltonian $H(x)$
is autonomous. For the sake of simplicity, we shall also assume that it
is $C^{1}$.

>>>>

\keywords{}
\end{abstract}
%
\section{Introduction} \label{sec:intro}
%
%
\section{Where in Practice} \label{sec:practice}
\section{Low Discrepancy Sequence Constructions} \label{sec:construct}
\section{Discrepancy} \label{sec:discrepancy}
\section{Stopping Criteria} \label{sec:stop}
\section{Reformulating Our Problem} \label{sec:reformulate}
\section{Ongoing Research} \label{sec:onging}
\section{Conclusion} \label{sec:conclusion}

\end{document}
%
In this section, we will consider the case when the Hamiltonian $H(x)$
is autonomous. For the sake of simplicity, we shall also assume that it
is $C^{1}$.
